%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Firmware Engineer} % Job title
    {Starling Medical} % Organization
    {Houston, Texas} % Location
    {Nov. 2022 - Dec. 2023} % Date(s)
    {
      \begin{cvitems}
        \item {Collaborated with a 9-person, Y Combinator-backed team to align app-device integration and UX.}
        \item {Sole developer for a IoT medical device's firmware, prototype to production, using Zephyr RTOS.}
        \item {Optimized power management for NRF9160 and NRF52840, achieving target 6+ months of operation time.}
        \item {Contributed to inventory and failure analysis for pilot devices, reduced LTE cellular signal failures by 48\%.}
        \item {Engineered Bluetooth Low Energy (BLE) services for communication with phone apps.}
        \item {Devised and executed a solution to AWS IoT-core cert signing, saving 5,000+ USD yearly operations costs.}
        \item {Leveraged sensor datasheet to extend Zephyr driver, increasing usable features from 60\% to 100\%.}
        \item {Coordinated communication between on-board components via UART/I2C/SPI/USB.}
        \item {Shipped multiple packages to factory in China, valued in excess of 8,000 USD.}
        \item {Acted as liason for Chinese manufacturer via WeChat and email.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data \& Infrastructure Engineer} % Job title
    {SLB (formerly Schlumberger)} % Organization
    {Houston, Texas} % Location
    {Jun. 2022 - Nov. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Delivered excellent service to international clients to ensure 100\% customer satisfaction with company’s data management software.}
        \item {Orchestrated calls via Teams to connect clients with expert team members, exceeding target satisfaction of 75\% quarterly.}
        \item {Employed Dataiku to create endpoints for ETL and machine learning (ML) model queries, leading to 2\% boost in efficiency of existing data processes.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Business Alliance Financial Services (BAFS)} % Organization
    {Ruston, Louisiana} % Location
    {Nov. 2017 - Mar. 2020} % Date(s)
    {
      \begin{cvitems}
        \item {Aided initial development of a business loan-servicing application, now serving 250+ clients nationally.}
        \item {Assembled error-checking/alert service in Python to ensure nightly database updates run smoothly.}
        \item {Expanded and refined filtering/ETL functionality to Python API, increasing capabilities of service by 5\%.}
        \item {Constructed web views using JavaScript \& React, contributing to 10\% of production frontend code.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Fellow} % Job title
    {United States Air Force / Louisiana Tech Research Institute (LTRI)} % Organization
    {Ruston, Louisiana} % Location
    {Jun. 2020 - May. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Co-lead team to develop a multi-module system for digital twinning of simulations and real events in a 5-minute window.}
        \item {Established foundational project management protocols for team, increasing productivity 60\%.}
        \item {Deployed onboarding curriculum via lectures and workshops to build programming skills \& best practices for 4 undergraduate team members.}
        \item {Lead efforts to understand existing C++ source code.}
        \item {Formulated a program for generation and use of geolocation data based on VOACAP radio data with Python/MongoDB, improving simulation accuracy by 20\%.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Associate Consultant} % Job title
    {Fenway Group} % Organization
    {Ruston, Louisiana} % Location
    {Apr. 2017 - Nov. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contracted out to a large healthcare company with 120,000+ member userbase.}
	      \item {Constructed dashboards and pivot tables in Splunk for error reporting heuristics, reducing downtime and increasing corrections rate.}
        \item {Leveraged Actian DataConnect ad SQL queries for ETL.}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}

%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Academic Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Research Associate} % Job title
    {Louisiana Tech University} % Organization
    {Ruston, Louisiana} % Location
    {Jun. 2021 - Aug. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Joined a small team making a modular netowork traffic filtering software for Linux(Ubuntu server).}
	      \item {Created logging and alert services using MQTT, MySQL, libcurl, curl, C++, Twilio SMS, and SendGrid}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Graduate Student} % Job title
    {Louisiana Tech University} % Organization
    {Ruston, Louisiana} % Location
    {Aug. 2020 - May. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and Tested Android malware against Oculus Quest 2}
	      \item {Executed SRS testing malware sample using Android Studio/Gradle/Kotlin.}
        \item {Proved viability of ransomware on VR headset.}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
