%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Echo | Project lead} % Proj name
{Local-compute-only AI voice assistant} % summary
{\href{https://github.com/JohnnySn0w/Echo}{\textbf{GitHub}}} % Location
{Feb. 2024 - Current} % Date(s)
{
  \begin{cvitems} % Description(s) bullet points
    \item{Orchestrating the implementation of an AI stack reliant solely on local computational resources, enhancing privacy and response times.}
    \item{Spearheading a diverse team through the complexities of system architecture and software development, fostering innovation and teamwork.}
    \item{Innovating a conversational interface allowing secure, offline voice interactions, leveraging voice synthesis to simulate real-time discourse.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{MoD | Lead on capstone group project} % Proj name
{Using Node.js to implement a Multi-User Dungeon on Discord} % summary
{\href{https://github.com/JohnnySn0w/MoD}{\textbf{GitHub}}} % Location
{Nov. 2019 - May 2020} % Date(s)
{
  \begin{cvitems} % Description(s) bullet points
    \item{Secured project approval and led a six-member team in developing a bespoke MUD engine that integrates with Discord, enhancing user engagement.}
    \item{Engineered a highly scalable, serverless backend using DynamoDB, achieving robust performance and reliability.}
    \item{Instituted a modular design allowing for dynamic content updates, significantly enhancing game flexibility and player creativity.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{ArXver | Personal project} % Proj name
{Webscraping tweets for archival} % summary
{\href{https://github.com/JohnnySn0w/ArXver}{\textbf{GitHub}}} % Location
{Jan. 2024} % Date(s)
{
  \begin{cvitems} % Description(s) bullet points
    \item{Developed a sophisticated tool for archiving Twitter content into Markdown, facilitating easy integration with personal knowledge management systems like Obsidian.}
    \item{Automated content tagging and organization using advanced web scraping and parsing techniques, streamlining data retrieval and utilization.}
    \item{Synthesis of Python web scraping, JSON parsing, Markdown templating, and HTML arrangement.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{88x31 Collager | Personal project} % Proj name
{Art generation tool using Geocities banner archive} % summary
{\href{https://github.com/JohnnySn0w/8831-collager}{\textbf{GitHub}}} % Location
{Mar. 2024 - Apr. 2024} % Date(s)
{
  \begin{cvitems} % Description(s) bullet points
    \item{Created a unique video generation tool that transforms pixels into banner art, employing Python and libraries such as Pillow and ImageMagick for artistic content creation.}
    \item{Leveraged multiprocessing and shared memory techniques in Python, optimizing performance and resource utilization.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Network filtering softare | Team member} % Job title
{Modular packet filtering system} % Organization
{Louisiana Tech University} % Location
{Jun. 2021 - Aug. 2021} % Date(s)
{
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Contributed to the development of an innovative network traffic filtering solution for Linux servers, enhancing network security and performance.}
        \item{Designed and implemented comprehensive logging and alert systems, incorporating a variety of technologies (MQTT, MySQL, C++) to ensure real-time monitoring and response.}
    \end{cvitems}
}

%---------------------------------------------------------

\cventry
{Simple Ransomware Sample | Thesis work} % Job title
{Study and generation of ransomware samples} % Organization
{\href{https://github.com/JohnnySn0w/SRS}{\textbf{GitHub}}} % Location
{Aug. 2020 - May. 2022} % Date(s)
{
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Conducted groundbreaking research on the feasibility of ransomware attacks on VR headsets, specifically Oculus Quest 2, demonstrating significant vulnerabilities.}
        \item{Employed Android Studio and Kotlin to simulate ransomware attacks, contributing valuable insights into VR security challenges.}
    \end{cvitems}
}

%---------------------------------------------------------
\end{cventries}
